paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

---
title: "paper_replication"
output: pdf_document
---
### Importance
In the United States, many state legislatures have enacted a range of laws limiting access to abortions.  These laws limit access to crucial healthcare and have impacts on mortality, fertility, and birth rates across the country.

@@

### Conclusions and Relevance

>>>>

---
title: "paper_replication"
output: pdf_document
---
## Abstract
### Importance
In the United States, many state legislatures have enacted a range of laws limiting access to abortions.  These laws limit access to crucial healthcare and have impacts on mortality, fertility, and birth rates across the country.

@@

### Conclusions and Relevance
Our analysis confirms the results of Brown et al. showing a negative association between restrictive abortion legislation and abortion rates based on both the 18 states they analyized and based on data from all 50 states.  We furthered the analysis to additional outcomes and found positive associations between restrictions and infant death rates.
